\documentclass[paper=a4, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size

\newcommand{\assignment}{6}
\newcommand{\duedate}{March 29, 2023}
\input{latex-include/hw-template.tex}
\author{
    \textbf{YOUR NAME} \\ 
    \textbf{YOUR GIT USERNAME} \\ 
    \textbf{YOUR E-MAIL}
}% INFORMATION

\begin{document}

\maketitle % Print the title

% Convert to DOCX using https://pdf2docx.com/

Your assignment for this week will be to send us a 2-page project proposal. The Google Docs version of this proposal is available \href{https://docs.google.com/document/d/14Mr8ed5dXt-zEOOucCBdzhDnmKYgnMIx}{here}. You can choose the format you want to use, but make sure to include the following information to your document:

\begin{enumerate}
    \item What problem are you going to be tackling on your project?
    \item Why is that an interesting/useful application of data mining?
    \item What models/techniques (clustering/classification/etc.) are you envisioning to apply?
    \item Where are you going to get the data?
\end{enumerate}

To complete your proposal submission, create your project's repository in your own Github namespace, and upload your provide your URL in Gradescope. For example, my Git handle is \verb"kni-neu", and my project repository is:

\begin{verbatim}
    https://github.com/kni-neu/project
\end{verbatim}

You can use my template or any other template that you might find appropriate. (Or, it is acceptable to use no template at all.) An example of a set of organized proposal sections is shown below.

\section{Problem}
Make sure you make clear what problem are you going to solve in as concise and unambiguous manner. This section is typically 2-3 sentences.

\section{Background} 
This is where you tell us why this solving this problem is important. What will people be able to do once you've solved this problem? How could it conceivably help people? What makes this application of data mining  useful?

\section{Approach}

Here, you can start detailing some specifics. Be sure to cover:

\begin{itemize}
    \item Where are you going to get data? 
    \item What data mining techniques will you use?
\end{itemize}


\end{document}
